---
title: "Boston House Price"
subtitle: "Final Project"
author: 
  - "Baiheng Zhou --- Seunghyun Lee --- Zijun Shi"
  - "Jun Zhang --- Yoffie Wu"
  - "--------------------------------------------"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true 
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

```{r xaringan-animate-css, echo=FALSE}
xaringanExtra::use_animate_css()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
library(gt)
url = "https://raw.githubusercontent.com/DATA2002/data/master/boston.csv"
boston_data = readr::read_csv(url)
```

# Data overview 

```{r}
dim(boston_data)
glimpse(boston_data)
```

---

# Data visualization

```{r, message=FALSE, echo=FALSE}
library(GGally)
ggpairs(boston_data)
```

```{r, echo=FALSE}
n = 506
k = 13
2^k
cor_mat = cor(boston_data)
melted_cor_mat = cor_mat %>%
  data.frame() %>% 
  rownames_to_column(var = "var1") %>% 
  gather(key = "var2", value = "cor", -var1)
ggplot(data = melted_cor_mat, 
       aes(x=var1, y=var2, fill=cor)) + 
geom_tile() + theme_minimal() +
scale_fill_gradient2(
    low = "blue", high = "red", mid = "white", 
    midpoint = 0, limit = c(-1,1)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

---

# Basic model (without any transformation) 

```{r}
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
round(summary(M1)$coef, 3)
t(round(broom::glance(M1), 2)) #adjusted rsquared : 0.73
```

```{r}
#AIC  backward searching 
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
step.back.aic = step(M1, direction = "backward", trace = FALSE)
step.back.aic %>% broom::glance() %>% round(2) %>% t()
drop1(step.back.aic , test = "F")
t(round(broom::glance(step.back.aic), 2))
# we removed (indus, age), adjusted r.squared : 0.73
```

```{r}
#AIC forward searching 
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
step.fwd.aic = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
add1(step.fwd.aic, test="F", scope = M1)
t(round(broom::glance(step.fwd.aic), 2)) 
# we removed (indus, age), adjusted r-squared : 0.73
```

---

# Log transformation :  MEDV, B, LSTAT, DIS, NOX

For Linearity assumption, this report used log transformation. 

```{r, message=FALSE, echo=FALSE}
boston_data = readr::read_csv(url)
boston_data = boston_data %>% 
  mutate(MEDV = log(MEDV)) 
boston_data = boston_data%>%
  mutate(B = log(B))
boston_data = boston_data%>%
  mutate(LSTAT = log(LSTAT))
boston_data = boston_data%>%
  mutate(DIS = log(DIS))
boston_data = boston_data%>%
  mutate(NOX = log(NOX))
ggpairs(boston_data)
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
round(summary(M1)$coef, 3)
t(round(broom::glance(M1), 2)) #ADJUSTED r squared : 0.80
```

```{r}
#AIC  backward searching 
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
step.back.aic = step(M1, direction = "backward", trace = FALSE)
round(summary(step.back.aic)$coef, 3)
drop1(step.back.aic , test = "F")
t(round(broom::glance(step.back.aic), 2))
# we removed (zn, indus, age), adjusted r-squared : 0.80
```


```{r}
#AIC forward searching 
M0 = lm(MEDV ~ 1, data = boston_data)  # Null model
M1 = lm(MEDV ~ ., data = boston_data)  # Full model
step.fwd.aic = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
add1(step.fwd.aic, test="F", scope = M1)
t(round(broom::glance(step.fwd.aic), 2)) 
# we removed (zn, indus, age), adjusted r-squared : 0.80
```

```{r}
stepm = step(M1)
```

```{r}
stepm
```

---

# Assumption checking 

.panelset[
.panel[.panel-name[Linearity]

```{r panel-chunk1,fig.align='center',fig.width = 16,fig.height = 6.75, fig.retina=2, fig.align='center', warning=FALSE, echo=FALSE, message=FALSE}

library(tidyverse)
lrm = boston_data %>% 
  ggplot(aes(x = RM, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_smooth(method = "lm", se = T) + 
  theme_grey(base_size = 8) + 
  ggtitle("average number of rooms per dwelling") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

lnox = boston_data %>% 
  ggplot(aes(x = NOX, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_smooth(method = "lm", se = T) + 
  theme_grey(base_size = 8) + 
  ggtitle("Charles River dummy variable") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

ldis = boston_data %>% 
  ggplot(aes(x = DIS, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = T) + 
  theme_grey(base_size = 8) + 
  ggtitle("weighted distances to five Boston employment centres") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

ltax = boston_data %>% 
  ggplot(aes(x = TAX, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = T) +  
  theme_grey(base_size = 8) + 
  ggtitle("full-value property-tax rate per $10,000") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

lptra = boston_data %>% 
  ggplot(aes(x = PTRATIO, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = T) + 
  theme_grey(base_size = 8) + 
  ggtitle("pupil-teacher ratio by town") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

llstat = boston_data %>% 
  ggplot(aes(x = LSTAT, y = MEDV)) + 
  geom_point(size = 0.3) + 
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = T) + 
  theme_grey(base_size = 8) + 
  ggtitle("% lower status of the population") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  ylim(1, 4.5)

gridExtra::grid.arrange(lrm, lnox, ldis, ltax, lptra, llstat, ncol = 3, nrow = 2)

```

]

.panel[.panel-name[Normality]

```{r panel-chunk2,fig.align='center',fig.width = 16,fig.height = 6.75, fig.retina=2, fig.align='center', warning=FALSE, echo=FALSE, message=FALSE}

q1 = boston_data %>% ggplot(aes(sample = RM)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("RM") + 
  theme(plot.title = element_text(size = 10, face = "bold")) + 
  theme_grey(base_size = 8)

q2 = boston_data %>% ggplot(aes(sample = NOX)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("NOX") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme_grey(base_size = 8)

q3 = boston_data %>% ggplot(aes(sample = DIS)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("DIS") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme_grey(base_size = 8)

q4 = boston_data %>% ggplot(aes(sample = TAX)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("TAX") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme_grey(base_size = 8)

q5 = boston_data %>% ggplot(aes(sample = PTRATIO)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("PTRATIO") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme_grey(base_size = 8)

q6 = boston_data %>% ggplot(aes(sample = LSTAT)) + 
  geom_qq() + 
  geom_qq_line() + 
  ggtitle("LSTAT") + 
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme_grey(base_size = 8)

gridExtra::grid.arrange(q1, q2, q3, q4, q5, q6, ncol = 3, nrow = 2)

```

]

.panel[.panel-name[Total Performance]

```{r panel-chunk3,fig.align='center',fig.width = 16,fig.height = 6.75, fig.retina=2, fig.align='center', warning=FALSE, echo=FALSE, message=FALSE}

library(ggfortify)
autoplot(stepm, which = 1:2) + theme_bw()

```

]
]

---

# Question 

-how are we going to deal with non -linear variables? like CHAS, RAD, TAX
