---
title: "final process"
author: "Baiheng Zhou"
date: "10/27/2021"
output:
  html_document:
    fig_caption: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 4
    toc_width: 6
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to Boston House Price data

```{r}

library(tidyverse)
library(knitr)
library(gt)
url = "https://raw.githubusercontent.com/DATA2002/data/master/boston.csv"
boston_data = readr::read_csv(url)

```

```{r, message=FALSE}

boston_data = boston_data %>%
  mutate(LMEDV = log(MEDV))

```


# 1. Create Full Model

```{r}

M0 = lm(LMEDV ~ 1, data = boston_data)  # Null model
M1 = lm(LMEDV ~ . - MEDV, data = boston_data)  # Full model

round(summary(M1)$coef, 3)

```

```{r}

library(ggfortify)
autoplot(M1, which = 1:2) + theme_bw()

```

# 2. Assumption testing for full model (make sure it satisfies the assumption)

- Linearity 
-- pass
- Independence 
-- The origin of the boston housing data is Natural
- Homoskedasticity 
-- Data above the line and under the line have similar numbers
- Normality pass
-- QQ plot follow the

# 3. Create model by using AIC

```{r}

stepm = step(M1)

```

```{r}

stepm

```

```{r}

library(ggfortify)
autoplot(stepm, which = 1:2) + theme_bw()

```

# 4. Find the best model

```{r}

library(caret)

control = trainControl(method = "repeatedcv", number = 10, repeats = 10)

step_model = LMEDV ~ CRIM + ZN + CHAS + NOX + RM + DIS + RAD + TAX + PTRATIO + B + LSTAT
full_model = LMEDV ~ CRIM + ZN + INDUS + CHAS + NOX + RM + AGE + DIS + RAD + TAX + PTRATIO + B + LSTAT
simple_model = LMEDV ~ CRIM

step_cv = train(step_model, method = "lm", data = boston_data, trControl = control)
full_cv = train(full_model, method = "lm", data = boston_data, trControl = control)
simple_cv = train(simple_model, method = "lm", data = boston_data, trControl = control)

results <- resamples(list(simple = simple_cv,
                          step = step_cv,
                          full = full_cv))
summary(results)

p1 = ggplot(results, metric = "RMSE") +
  theme_classic() +
  labs(y = "RMSE")

p2 = ggplot(results, metric = "MAE") +
  theme_classic() +
  labs(y = "MAE")

cowplot::plot_grid(p1, p2, ncol = 1)

```

# 5. Assumption testing for the best model

Step_model is a little bit better than full_model.

- Linearity 
-- pass
- Independence 
-- The origin of the boston housing data is Natural
- Homoskedasticity 
-- Data above the line and under the line have similar numbers
- Normality pass
-- QQ plot follow the

